---
title: <font size="5">**Tactile information counteracts the attenuation of rubber hand illusion attributable to increased visuo-proprioceptive divergence**</font> 
author: <br> <font size="4"> Piotr Litwin & Paweł Motyka (University of Warsaw) </font> 
date: <font size="3"> September 2020  </font>
output: html_document
chunk_output_type: console
--- 
&nbsp;

<font size="4">
**List of sections**:

1. Load the required packages and data [S1](#S1)
2. Data preparation [S2](#S2)
3. Descriptives [S3](#S3)
4. Non-parametric analyses  [S4](#S4)
5. LQMM analyses  [S5](#S5)
6. Back-transformation of logit-score coefficients [S6](#S6)
7. Correlations and corrplots [S7](#S7)
8. Supplementary material plots [S8](#S8)

--- 

<a name="S1"></a>
&nbsp;

#####**1. Load required packages and data**  

```{r, message=FALSE, warning= FALSE}

library(dplyr)
library(data.table)
library(car)
library(here)
library(colorspace)
library(ggplot2)
#data directory & data reading
data_dir <- paste0(here())
setwd(data_dir)

library(readxl)
db <- read_excel("RHI_TD_data.xlsx")

```

<a name="S2"></a>
&nbsp;

#####**2. Data preparation** 

```{r, warning= FALSE}

### BASIC DATA PREPARATION

db[db == 99] <- NA
db$drift <- db$drift_post - db$drift_pre
db$illusion <- (db$q1 + db$q2 + db$q3) / 3
db$control <- (db$q4 + db$q5 + db$q6) / 3

# filter drift and proprioceptive accuracy outliers

db$z_drift <- (db$drift - mean(db$drift,na.rm=TRUE)) / sd(db$drift,na.rm = TRUE)
db$drift <- ifelse(between(db$z_drift,-2,2),db$drift,NA)

db$z_threshold <- (db$threshold - mean(db$threshold,na.rm=TRUE)) / sd(db$threshold,na.rm = TRUE)
db$threshold <- ifelse(between(db$z_threshold,-2,2),db$threshold,NA)

db$z_sigma <- (db$sigma - mean(db$sigma,na.rm=TRUE)) / sd(db$sigma,na.rm = TRUE)
db$sigma <- ifelse(between(db$z_sigma,-2,2),db$sigma,NA)

# center threshold and sigma variables for interaction analyses

db$threshold.c=db$threshold-mean(db$threshold,na.rm=TRUE)

db$sigma.c=db$sigma-mean(db$sigma,na.rm=TRUE)

# code distance and complexity as factors

db$distance=as.factor(db$distance)
db$compl=as.factor(db$compl)


### LOGIT TRANSFORMATION OF DEPENDENT VARIABLE FOR LQMM 

db$illusionLogit <- log((db$illusion+3.001)/(3.001-db$illusion)) # The small quantity == 0.001 ensures that the logistic transform is defined for all values of the illusion score

### FILTER RHI NON-RESPONDERS

dbR = db

# Filter non-responders 

for (p in unique(dbR$ID)) {
  dbR$responder[dbR$ID == p & dbR$illusion >= 1] <- T
  dbR$ID[db$ID == p] <- gsub('[^0-9]', '', p)

}

dbR$ID <- as.numeric(as.character(dbR$ID))

responders_list <- unique(dbR$ID[dbR$responder == T])
sample <- length(na.omit(responders_list))
sample 

dbR <- subset(dbR, ID %in% responders_list)

length(unique(dbR$ID))

```

#####**3. Descriptives

```{r, message=FALSE, warning= FALSE}

# find participants for at least one drift observation was excluded / find proprioceptive acuity outliers

drifters = base::unique(unique(dbR$ID[dbR$z_drift > 2 | dbR$z_drift < -2]))
thresholders = base::unique(unique(dbR$ID[dbR$z_threshold > 2 | dbR$z_threshold < -2]))
sigmers = base::unique(unique(dbR$ID[dbR$z_sigma > 2 | dbR$z_sigma < -2]))

# DESCRIPTIVES 

# subjective RHI scores - illusion + control
rhimeans = aggregate(illusion ~ compl*distance, data=dbR, mean)
rhisds = aggregate(illusion ~ compl*distance, data=dbR, sd)

controlmeans = aggregate(control ~ compl*distance, data=dbR, mean)
controlsds = aggregate(control ~ compl*distance, data=dbR, sd)

# drift
driftmeans = aggregate(drift ~ compl*distance, data=dbR, mean)
driftsds = aggregate(drift ~ compl*distance, data=dbR, sd)


```

<a name="S3"></a>
&nbsp;

#####**4. Nonparametric analyses** 

```{r, warning= FALSE}

# create one data-base per RHI elicitation condition

C1 <- dplyr::select(filter(dbR, compl == 1 & distance == 1),c(ID,illusion,control,threshold,sigma,drift,illusionLogit))
C2 <- dplyr::select(filter(dbR, compl == 2 & distance == 1),c(ID,illusion,control,threshold,sigma,drift,illusionLogit))
C3 <- dplyr::select(filter(dbR, compl == 3 & distance == 1),c(ID,illusion,control,threshold,sigma,drift,illusionLogit))
C4 <- dplyr::select(filter(dbR, compl == 1 & distance == 2),c(ID,illusion,control,threshold,sigma,drift,illusionLogit))
C5 <- dplyr::select(filter(dbR, compl == 2 & distance == 2),c(ID,illusion,control,threshold,sigma,drift,illusionLogit))
C6 <- dplyr::select(filter(dbR, compl == 3 & distance == 2),c(ID,illusion,control,threshold,sigma,drift,illusionLogit))

# paired Wilcoxon tests for the difference between illusion and control RHI scores in all six conditions
  
C1wil=wilcox.test(C1$illusion,C1$control,paired=TRUE)
C2wil=wilcox.test(C2$illusion,C2$control,paired=TRUE)
C3wil=wilcox.test(C3$illusion,C3$control,paired=TRUE)
C4wil=wilcox.test(C4$illusion,C4$control,paired=TRUE)
C5wil=wilcox.test(C5$illusion,C5$control,paired=TRUE)
C6wil=wilcox.test(C6$illusion,C6$control,paired=TRUE)
pvals=c(C1wil$p.value*6,C2wil$p.value*6,C3wil$p.value*6,C4wil$p.value*6,C5wil$p.value*6,C6wil$p.value*6) #bonferroni-corrected p values

# friedman test for control scores
dbR$condition<-ifelse(dbR$distance==1 & dbR$compl==1, 1,
                      ifelse(dbR$distance==1 & dbR$compl==2, 2,
                             ifelse(dbR$distance==1 & dbR$compl==3, 3,
                                    ifelse(dbR$distance==2 & dbR$compl==1, 4,
                                           ifelse(dbR$distance==2 & dbR$compl==2, 5,
                                                  ifelse(dbR$distance==2 & dbR$compl==3, 6, NA))))))

friedman.test(control~condition |ID, data=dbR)  
  
# paired Wilcoxon tests for distance effects in three touch conditions

notouch=wilcox.test(illusion~distance,data=dbR,subset= compl==1, paired=TRUE, correct=TRUE, exact=FALSE, conf.int=TRUE) 
simpletouch=wilcox.test(illusion~distance,data=dbR,subset= compl==2, paired=TRUE, correct=TRUE, exact=FALSE, conf.int=TRUE) 
complextouch=wilcox.test(illusion~distance,data=dbR,subset= compl==3, paired=TRUE, correct=TRUE, exact=FALSE, conf.int=TRUE)

# obtain Z scores
library(rcompanion)
wilcoxonZ(dbR$illusion[dbR$compl==1&dbR$distance==1],dbR$illusion[dbR$compl==1&dbR$distance==2],paired=TRUE,correct=TRUE)
wilcoxonZ(dbR$illusion[dbR$compl==2&dbR$distance==1],dbR$illusion[dbR$compl==2&dbR$distance==2],paired=TRUE,correct=TRUE)
wilcoxonZ(dbR$illusion[dbR$compl==3&dbR$distance==1],dbR$illusion[dbR$compl==3&dbR$distance==2],paired=TRUE,correct=TRUE)

# effect sizes - matched-pairs rank-biserial correlations (Kerby, 2014)

dbRnotouch=subset(dbR,compl==1)
dbRsimple=subset(dbR,compl==2)
dbRcomplex=subset(dbR,compl==3)

wilcoxonPairedRC(x=dbRnotouch$illusion,g=dbRnotouch$distance)
wilcoxonPairedRC(x=dbRsimple$illusion,g=dbRsimple$distance)
wilcoxonPairedRC(x=dbRcomplex$illusion,g=dbRcomplex$distance)

# plot results 
red <- darken("#F8766D", amount = 0.35)
blue <- darken("dodgerblue3", amount = 0.4)
br <- c(1,3,6,9,12)

t1 <- dbR[dbR$compl == "1",]

t1p <- ggplot(t1, aes(x=factor(distance), y=illusion, fill=factor(distance)) ) + geom_count(aes(colour=factor(distance)), show.legend = TRUE, alpha=0.5) +  scale_size_area(breaks = br) + geom_boxplot(width = 0.45, alpha = 0.5, show.legend = FALSE, outlier.shape = NA) + scale_color_manual(values=c(red, blue)) + scale_fill_manual(values=c(red, blue)) + labs(x = "Distance" , y = "Illusion Strength") + scale_y_continuous(limits= c(-3, 3), breaks = c(-3,-2,-1,0,1,2, 3), expand = c(0.05,0.05)) + scale_x_discrete(labels = c('Close','Far')) + theme_classic() + theme(axis.text.y = element_text(face = "bold", size = 13, color = "black"), axis.text.x = element_text(face = "bold", size = 11, color = "black"), legend.title=element_text(size=11), legend.text=element_text(size=10), axis.title.y = element_text(margin = margin(t = 0, r = 9, b = 0, l = 0)), axis.title.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)))

t1p
# export size (4, 5)

t2 <- dbR[dbR$compl == "2",]

t2p <- ggplot(t2, aes(x=factor(distance), y=illusion, fill=factor(distance)) ) + geom_count(aes(colour=factor(distance)), show.legend = TRUE, alpha=0.5) +  scale_size_area(breaks = br) + geom_boxplot(width = 0.45, alpha = 0.5, show.legend = FALSE, outlier.shape = NA) + scale_color_manual(values=c(red, blue)) + scale_fill_manual(values=c(red, blue)) + labs(x = "Distance" , y = "Illusion Strength") + scale_y_continuous(limits= c(-3, 3), breaks = c(-3,-2,-1,0,1,2, 3), expand = c(0.05,0.05)) + scale_x_discrete(labels = c('Close','Far')) + theme_classic() + theme(axis.text.y = element_text(face = "bold", size = 13, color = "black"), axis.text.x = element_text(face = "bold", size = 11, color = "black"), legend.title=element_text(size=11), legend.text=element_text(size=10), axis.title.y = element_text(margin = margin(t = 0, r = 9, b = 0, l = 0)), axis.title.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)))

t2p


t3 <- dbR[dbR$compl == "3",]

t3p <- ggplot(t3, aes(x=factor(distance), y=illusion, fill=factor(distance)) ) + geom_count(aes(colour=factor(distance)), show.legend = TRUE, alpha=0.5) +  scale_size_area(breaks = br) + geom_boxplot(width = 0.45, alpha = 0.5, show.legend = FALSE, outlier.shape = NA) + scale_color_manual(values=c(red, blue)) + scale_fill_manual(values=c(red, blue)) + labs(x = "Distance" , y = "Illusion Strength") + scale_y_continuous(limits= c(-3, 3), breaks = c(-3,-2,-1,0,1,2, 3), expand = c(0.05,0.05)) + scale_x_discrete(labels = c('Close','Far')) + theme_classic() + theme(axis.text.y = element_text(face = "bold", size = 13, color = "black"), axis.text.x = element_text(face = "bold", size = 11, color = "black"), legend.title=element_text(size=11), legend.text=element_text(size=10), axis.title.y = element_text(margin = margin(t = 0, r = 9, b = 0, l = 0)), axis.title.x = element_text(margin = margin(t = 5, r = 0, b = 0, l = 0)))

t3p

```

<a name="S4"></a>
&nbsp;

#####**5. LQMM analyses** 

```{r, warning= FALSE}

library(lqmm)

# specify control parameters

mintControl = lqmmControl(method="gs", LP_max_iter = 1000, UP_max_iter = 50) #gradient search optimization, increased number of max iterations to ensure that the algorithm converges

# Model 1: distance x complexity

mint = lqmm(fixed = illusionLogit ~ distance * compl, random = ~1, group = ID, tau = c(0.25,0.5,0.75), na.action = na.omit, data = dbR, control=mintControl)

modelHYP1 = summary(mint, R = 200) # increase number of bootstrap iterations to 200 to provide more stable estimations of parameters given relatively low number of predictors : sample size ratio

# Model 2: distance x complexity x threshold.c

mintthresh = lqmm(fixed = illusionLogit ~ distance * compl * threshold.c, random = ~1, group = ID, tau = c(0.25,0.5,0.75), na.action = na.omit, data = dbR, control=mintControl)

# Model 2: distance x complexity x sigma.c

modelHYP2.1 = summary(mintthresh, R = 200)

mintsigma = lqmm(fixed = illusionLogit ~ distance * compl * sigma.c, random = ~1, group = ID, tau = c(0.25,0.5,0.75), na.action = na.omit, data = dbR, control=mintControl)

modelHYP2.2 = summary(mintsigma, R = 200)

```

<a name="S5"></a>
&nbsp;

#####**6. Back-transformation of logit-score coefficients** 


```{r, warning= FALSE}

sums = modelHYP1

# coefficients at different taus

coefs25 = 3.001*((exp(1)**sums$tTable$`0.25`[,1])-1)/((exp(1)**sums$tTable$`0.25`[,1])+1) 
# dbR$illuScore = 3.001*((exp(1)**dbR$illusionLogit)-1)/((exp(1)**dbR$illusionLogit)+1) shows that the transformation is correct 
coefs50 = 3.001*((exp(1)**sums$tTable$`0.5`[,1]-1)/(exp(1)**sums$tTable$`0.5`[,1]+1))
coefs75 = 3.001*((exp(1)**sums$tTable$`0.75`[,1]-1)/(exp(1)**sums$tTable$`0.75`[,1]+1))

coefs = c(coefs25,coefs50,coefs75)

# standard deviations at different taus

sds25 = 3.001*(exp(1)**sums$tTable$`0.25`[,2]-1)/(exp(1)**sums$tTable$`0.25`[,2]+1)
sds50 = 3.001*(exp(1)**sums$tTable$`0.5`[,2]-1)/(exp(1)**sums$tTable$`0.5`[,2]+1)
sds75 = 3.001*(exp(1)**sums$tTable$`0.75`[,2]-1)/(exp(1)**sums$tTable$`0.75`[,2]+1)

sds = c(sds25,sds50,sds75)

# lower bounds of confidence intervals at different taus

lwrint25 = 3.001*(exp(1)**sums$tTable$`0.25`[,3]-1)/(exp(1)**sums$tTable$`0.25`[,3]+1)
lwrint50 = 3.001*(exp(1)**sums$tTable$`0.5`[,3]-1)/(exp(1)**sums$tTable$`0.5`[,3]+1)
lwrint75 = 3.001*(exp(1)**sums$tTable$`0.75`[,3]-1)/(exp(1)**sums$tTable$`0.75`[,3]+1)

lwrints = c(lwrint25,lwrint50,lwrint75)

# upper bounds of confidence intervals at different taus

uppint25 = 3.001*(exp(1)**sums$tTable$`0.25`[,4]-1)/(exp(1)**sums$tTable$`0.25`[,4]+1)
uppint50 = 3.001*(exp(1)**sums$tTable$`0.5`[,4]-1)/(exp(1)**sums$tTable$`0.5`[,4]+1)
uppint75 = 3.001*(exp(1)**sums$tTable$`0.75`[,4]-1)/(exp(1)**sums$tTable$`0.75`[,4]+1)

uppints = c(uppint25,uppint50,uppint75)

### COEFPLOTS 

library(arm)

# tau = 0.25

coefplot(coefs25,sds25,CI=2,lower.conf.bounds=lwrint25,upper.conf.bounds=uppint25,offset=0, vertical=FALSE,varnames=rownames(sums$tTable$`0.25`),  main="Estimated coefficients for 25th quantile (tau=0.25)", cex.pts = 1.4, var.las=1, ylim=c(-3,3))

# tau = 0.5

coefplot(coefs50,sds50,CI=2,lower.conf.bounds=lwrint50,upper.conf.bounds=uppint50,offset=0, vertical=FALSE,varnames=rownames(sums$tTable$`0.25`), main="Estimated coefficients for 50th quantile (tau=0.5)", cex.pts = 1.4, var.las=1, ylim=c(-3,3))

# tau = 0.75

coefplot(coefs75,sds75,CI=2,lower.conf.bounds=lwrint75,upper.conf.bounds=uppint75,offset=0, vertical=FALSE,varnames=rownames(sums$tTable$`0.25`), main="Estimated coefficients for 75th quantile (tau=0.75)", cex.pts = 1.4, var.las=1, ylim=c(-3,3))

```

<a name="S5"></a>
&nbsp;

#####**7. Correlations and corrplots ** 


```{r, warning= FALSE}

# proprioceptive acuity and illusion scores

propcor=data.table(C1$threshold,C1$sigma,C1$illusion,C2$illusion,C3$illusion,C4$illusion,C5$illusion,C6$illusion)
setnames(propcor,c("threshold","sigma","D1T1illusion","D1T2illusion","D1T3illusion","D2T1illusion","D2T2illusion","D2T3illusion"))

library(Hmisc)
library(corrplot)
propmat=rcorr(as.matrix(propcor), type="spearman")

col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot::corrplot(propmat$r, method="color", col=col(200),  
         type="upper", order="original", 
         addCoef.col = "black", 
         tl.col="black", tl.srt=45, 
         p.mat = propmat$P, sig.level = 0.05, insig = "blank", 
         diag=FALSE 
)

# drift and illusion scores

cor.test(C1$illusion,C1$drift,use="complete.obs", method="spearman")
cor.test(C2$illusion,C2$drift,use="complete.obs", method="spearman")
cor.test(C3$illusion,C3$drift,use="complete.obs", method="spearman")
cor.test(C4$illusion,C4$drift,use="complete.obs", method="spearman")
cor.test(C5$illusion,C5$drift,use="complete.obs", method="spearman")
cor.test(C6$illusion,C6$drift,use="complete.obs", method="spearman")

# drift and proprioceptive acuity indicators

driftcor=data.table(C1$drift,C2$drift,C3$drift,C4$drift,C5$drift,C6$drift)
setnames(driftcor,c("D1T1drift","D1T2drift","D1T3drift","D2T1drift","D2T2drift","D2T3drift"))
driftmat=rcorr(as.matrix(driftcor), type="pearson")

corrplot::corrplot(driftmat$r, method="color", col=col(200),  
                   type="upper", order="original", 
                   addCoef.col = "black", 
                   tl.col="black", tl.srt=45, 
                   p.mat = propmat$P, sig.level = 0.05, insig = "blank", 
                   diag=FALSE 
)

```

<a name="S5"></a>
&nbsp;

#####**8. Supplementary material plots** 


```{r, warning= FALSE}

library(ggplot2)

### RHI SCORES - BARPLOTS

x = list(rhimeans,controlmeans)
bilan=rbindlist(x,use.names=FALSE)
bilan=bilan %>% arrange(distance,compl)
bilan=as.data.frame(bilan)

barplot(bilan[,3], beside=T , legend.text=c("illusion", "control"),
                   col=c(rgb(0.1,0.6,0.1),
                         rgb(0.1,0.1,0.6)) , ylim=c(-3,3), xlim=c(0.4,7.2), cex.lab = 1.3, 
                   cex.axis = 1.5, width = 0.4, space=c(0.8,0))

# barplots with confidence intervals

x2 = list(rhisds,controlsds)
bilansds=rbindlist(x2,use.names=FALSE)
bilansds=bilansds %>% arrange(distance,compl)
bilansds=as.data.frame(bilansds)
bilansds[,3]=bilansds[,3]*1.96/sqrt(48) 

error.bar <- function(x, y, upper, lower=upper, length=0.03,...){
  arrows(x,y+upper, x, y-lower, angle=90, code=3, length=length, ...)
}

error.bar(barplot(bilan[,3], beside=T , legend.text=c("illusion", "control"),
                  col=c(rgb(0.1,0.6,0.1),
                        rgb(0.1,0.1,0.6)) , ylim=c(-3,3), xlim=c(0.4,7.2), cex.lab = 1.3, 
                  cex.axis = 1.5, width = 0.4, space=c(0.8,0)),bilan[,3],bilansds[,3])


### RHI SCORES - DISTRIBUTIONS (+ shapiro tests)

library(ggplot2)
par(mfrow = c(3, 2))

# define a function to arrange multiple plots (source: http://www.cookbook-r.com/Graphs/Multiple_graphs_on_one_page_(ggplot2))
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

red <- alpha(darken("#F8766D", amount = 0.35),0.7)
blue <- alpha(darken("dodgerblue3", amount = 0.4),0.7)

histd1t1=ggplot(subset(dbR,distance==1&compl==1), aes(x=illusion)) + geom_histogram(binwidth = 0.33333,color="black",fill=red) + geom_vline(aes(xintercept=mean(illusion)), color="black", linetype="dashed", size=1) + theme_classic() + ggtitle("D1:T1") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + scale_x_continuous(limits = c(-3.2,3.2), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(0,14), breaks = seq(0,14, by = 2)) + xlab("Illusion Score") + ylab("Count")
shapiro.test(dbR$illusion[dbR$distance==1&dbR$compl==1])

histd1t2=ggplot(subset(dbR,distance==1&compl==2), aes(x=illusion)) + geom_histogram(binwidth = 0.33333,color="black",fill=red) + geom_vline(aes(xintercept=mean(illusion)),color="black", linetype="dashed", size=1) + theme_classic() + ggtitle("D1:T2") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + scale_x_continuous(limits = c(-3.2,3.2), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(0,14), breaks = seq(0,14, by = 2))  + xlab("Illusion Score") + ylab("Count")
shapiro.test(dbR$illusion[dbR$distance==1&dbR$compl==2])

histd1t3=ggplot(subset(dbR,distance==1&compl==3), aes(x=illusion)) + geom_histogram(binwidth = 0.33333,color="black",fill=red) + geom_vline(aes(xintercept=mean(illusion)), color="black", linetype="dashed", size=1) + theme_classic() + ggtitle("D1:T3") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + scale_x_continuous(limits = c(-3.2,3.2), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(0,14), breaks = seq(0,14, by = 2))  + xlab("Illusion Score") + ylab("Count")
shapiro.test(dbR$illusion[dbR$distance==1&dbR$compl==3])

histd2t1=ggplot(subset(dbR,distance==2&compl==1), aes(x=illusion)) + geom_histogram(binwidth = 0.33333,color="black",fill=blue) + geom_vline(aes(xintercept=mean(illusion)), color="black", linetype="dashed", size=1) + theme_classic() + ggtitle("D2:T1") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + scale_x_continuous(limits = c(-3.2,3.2), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(0,14), breaks = seq(0,14, by = 2))  + xlab("Illusion Score") + ylab("Count")
shapiro.test(dbR$illusion[dbR$distance==2&dbR$compl==1])

histd2t2=ggplot(subset(dbR,distance==2&compl==2), aes(x=illusion)) + geom_histogram(binwidth = 0.33333,color="black",fill=blue) + geom_vline(aes(xintercept=mean(illusion)), color="black", linetype="dashed", size=1) + theme_classic() + ggtitle("D2:T2") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + scale_x_continuous(limits = c(-3.2,3.2), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(0,14), breaks = seq(0,14, by = 2))  + xlab("Illusion Score") + ylab("Count")
shapiro.test(dbR$illusion[dbR$distance==2&dbR$compl==2])

histd2t3=ggplot(subset(dbR,distance==2&compl==3), aes(x=illusion)) + geom_histogram(binwidth = 0.33333,color="black",fill=blue) + geom_vline(aes(xintercept=mean(illusion)),color="black", linetype="dashed", size=1) + theme_classic() + ggtitle("D2:T3") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + scale_x_continuous(limits = c(-3.2,3.2), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(0,14), breaks = seq(0,14, by = 2)) + xlab("Illusion Score") + ylab("Count")
shapiro.test(dbR$illusion[dbR$distance==2&dbR$compl==3])

multiplot(histd1t1, histd1t2, histd1t3, histd2t1,  histd2t2, histd2t3, cols = 2)
# export size: 5.5 x 7.5 

# SCATTERPLOTS - DRIFT AND ILLUSION SCORES

scatdriftC1 = ggplot(data = C1, aes(x = illusion, y = drift)) + geom_smooth(col = "black", size = 1, method = "lm", level=0.95, alpha = 0.5, fill = red) +     
  geom_point(col = red, alpha = 0.56, size = 3, shape = 18) + 
  theme_classic() + theme(axis.text=element_text(size=11)) + 
  ggtitle("D1:T1") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Illusion Score") + ylab("Drift") + 
  scale_x_continuous(limits = c(-3,3), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(-4,8), breaks = seq(-2.5,7.5, by = 2.5))

scatdriftC2 = ggplot(data = C2, aes(x = illusion, y = drift)) + geom_smooth(col = "black", size = 1, method = "lm", level=0.95, alpha = 0.5, fill = red) +     
  geom_point(col = red, alpha = 0.56, size = 3, shape = 18) + 
  theme_classic() + theme(axis.text=element_text(size=11)) + 
  ggtitle("D1:T2") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Illusion Score") + ylab("Drift") +
  scale_x_continuous(limits = c(-3,3), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(-4,8), breaks = seq(-2.5,7.5, by = 2.5))

scatdriftC3 = ggplot(data = C3, aes(x = illusion, y = drift)) + geom_smooth(col = "black", size = 1,method = "lm", level=0.95, alpha = 0.5, fill = red) +     
  geom_point(col = red, alpha = 0.56, size = 3, shape = 18) + 
  theme_classic() + theme(axis.text=element_text(size=11)) + 
  ggtitle("D1:T3") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Illusion Score") + ylab("Drift") +
  scale_x_continuous(limits = c(-3,3), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(-4,8), breaks = seq(-2.5,7.5, by = 2.5))

scatdriftC4 = ggplot(data = C4, aes(x = illusion, y = drift)) + geom_smooth(col = "black", size = 1, method = "lm", level=0.95, alpha = 0.5, fill = blue) +     
  geom_point(col = blue, alpha = 0.56, size = 3, shape = 18) + 
  theme_classic() + theme(axis.text=element_text(size=11)) + 
  ggtitle("D2:T1") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Illusion Score") + ylab("Drift") +
  scale_x_continuous(limits = c(-3,3), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(-4,8), breaks = seq(-2.5,7.5, by = 2.5))

scatdriftC5 = ggplot(data = C5, aes(x = illusion, y = drift)) + geom_smooth(col = "black", size = 1,method = "lm", level=0.95, alpha = 0.5, fill = blue) +     
  geom_point(col = blue, alpha = 0.56, size = 3, shape = 18) + 
  theme_classic() + theme(axis.text=element_text(size=11)) + 
  ggtitle("D2:T2") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Illusion Score") + ylab("Drift") +
  scale_x_continuous(limits = c(-3,3), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(-4,8), breaks = seq(-2.5,7.5, by = 2.5))

scatdriftC6 = ggplot(data = C6, aes(x = illusion, y = drift)) + geom_smooth(col = "black", size = 1, method = "lm", level=0.95, alpha = 0.5, fill = blue) +     
  geom_point(col = blue, alpha = 0.56, size = 3, shape = 18) + 
  theme_classic() + theme(axis.text=element_text(size=11)) + 
  ggtitle("D2:T3") + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + xlab("Illusion Score") + ylab("Drift") +
  scale_x_continuous(limits = c(-3,3), breaks = seq(-3,3, by = 1)) + scale_y_continuous(limits = c(-4,8), breaks = seq(-2.5,7.5, by = 2.5))

multiplot(scatdriftC1, scatdriftC2, scatdriftC3, scatdriftC4, scatdriftC5, scatdriftC6, cols = 2)
# export size: 6 x 8
```



